NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-07-28 paper/Chapters/Chapter3.tex
adding fig level 1 tables for model selection

@@

@@

	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

			Variables & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\

@@

			\multicolumn{4}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\ 
			\multicolumn{4}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\ 
			\multicolumn{4}{l}{DM, diabetes mellitus.}\\

@@

	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

		Variables & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\

@@

		\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\
		\multicolumn{5}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\
		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\

>>>>

%
%\rowcolors{2}{gray!6}{white}
%
%\begin{table}
%%	\captionsetup{font=small}
%	\caption{\label{tab:MLCA-level1}Level 1 classes comparison in the first step of MLCA. (All data, n = 6155, 24483 data points)}\vspace{-0.3cm}
%	\centering
%	\fontsize{9}{10}\selectfont
%	\begin{tabular}[t]{cccccccc}
%		\hiderowcolors
%		\toprule
%		\Centerstack{N of \\ classes} & \Centerstack{N of free \\ parameters} & log-likelihood & AIC & BIC & aBIC & Entropy & \Centerstack{ Lo-Mendel-Rubin \\ LRT}   \\
%		\midrule
%		\showrowcolors
%		1 & 48 & -372017.3 & 744130.6 & 744519.7 & 744367.1 & -- & --\\
%		2 & 97 & -368913.7 & 738021.4 & 738807.7 & 738499.4 & 0.777 & < 0.0001\\
%		3 & 146 & -366665.0 & 733621.9 & 734805.4 & 734341.4 & 0.666 & < 0.0001\\
%		4 & 195 & -365528.6 & 731447.1 & 733027.7 & 732408.0 & 0.658 & 0.8478\\
%		5 & 244 & -364901.2 & 730290.3 & 732268.1 & 731492.7 & 0.648 & 0.7602\\
%		6 & 293 & -363641.8 & 727869.5 & 730244.5 & 729313.4 & 0.701 & 0.7632\\
%		7 & 342 & -362789.9 & 726263.7 & 729035.9 & 727949.0 & 0.729 & 0.7702\\
%		8 & 391 & -362047.9 & 724877.9 & 728047.2 & 726804.6 & 0.737 & 0.8261\\
%		\bottomrule
%		\multicolumn{8}{l}{\textit{Note: }}\\
%		\multicolumn{8}{l}{\textbf{Abbreviations:} MLCA, multilevel class analysis; N, number; AIC, Akaike information criterion; BIC, }\\
%		\multicolumn{8}{l}{Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin}\\
%		\multicolumn{8}{l}{LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
%	\end{tabular}
%\end{table}
%
%\rowcolors{2}{white}{white}

\begin{figure}
	%\vspace*{13cm}
	\centering
	\includegraphics{Figures/class1mlcalevel1.png}
	\decoRule
	\caption[Level 1 Classes in MLCA]{Carbohydrate temporal eating patterns at observational day level.}
	\label{fig:MLCAfig1}
\end{figure}
%%\end{verbatim}

\rowcolors{2}{gray!6}{white}
\begin{table}

	\caption{\label{tab:}Fit Criteria for Each Model Specification}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
		\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
		\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
		\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
		\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Random effects model}}\\
		\hspace{1em}2 between classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
		\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
		\hspace{1em}3 between classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
		\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
		\hspace{1em}4 between classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
		\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
		\bottomrule
		\multicolumn{6}{l}{\textit{Note: }}\\
		\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing $q$ classes models with $q-1$ classes models.}\\
	\end{tabular}
\end{table}
\rowcolors{2}{white}{white}

@@

\begin{table}[h]

@@

	\caption{\label{tab:MLCAtab1}Means, percentages, and 95\% CIs of the characteristics  of carbohydrate temporal eating patterns by MLCA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

			 & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\

@@

			\multicolumn{4}{l}{\textbf{Abbreviations}: CI, confidence intervals; MLCA, multilevel latent class analysis; NDNS RP, national}\\ 
			\multicolumn{4}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
			\multicolumn{4}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\

@@

	\caption{\label{tab:LCGAtab1}Means, percentages, and 95\% CIs of the characteristics of carbohydrate temporal eating patterns by LCGA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

		 & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\

@@

		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; LCGA, latent class growth analysis; NDNS RP, national}\\ 
		\multicolumn{5}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
		\multicolumn{5}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\

### 2018-07-28 paper/Tables/2by2Table1.Rmd
adding fig level 1 tables for model selection

@@

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
# library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "latex", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)", 
      booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
# row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = c("Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;" ,
                       "Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with", 
                       "q-1 classes models."))
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_50_paper.csv", header = T)
names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
dt[is.na(dt)] <- ""
# library(formattable)

kable(dt, digits = 3, row.names = FALSE, align = "c",
      format = "latex", caption = "Fit Criteria for Each Model Specification", 
      booktabs = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_header_above(c(" ", "Number of level 1 classes" = 5)) %>% 
  group_rows("Fixed effects model", 1, 5) %>%
  group_rows("Random effects model", 6, 20) %>%
  add_indent(c(2:5,7:10,12:15,17:20)) %>% 
  footnote(general = c("Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models."))

```

### 2018-07-28 paper/Tables/2by2Table1.tex
adding fig level 1 tables for model selection

\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

>>>>

\caption{\label{tab:unnamed-chunk-2}Level 1 class selection. (All data, n = 6155, 24483 data points)}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccccc}
\hiderowcolors
\toprule
N of classes & N of free parameters & log-likelihood & AIC & BIC & aBIC & Entropy & Lo-Mendel-Rubin LRT\\
\midrule
\showrowcolors
1 & 48 & -372017.3 & 744130.6 & 744519.7 & 744367.1 & -- & --\\
2 & 97 & -368913.7 & 738021.4 & 738807.7 & 738499.4 & 0.777 & < 0.0001\\
3 & 146 & -366665.0 & 733621.9 & 734805.4 & 734341.4 & 0.666 & < 0.0001\\
4 & 195 & -365528.6 & 731447.1 & 733027.7 & 732408.0 & 0.658 & 0.8478\\
5 & 244 & -364901.2 & 730290.3 & 732268.1 & 731492.7 & 0.648 & 0.7602\\
6 & 293 & -363641.8 & 727869.5 & 730244.5 & 729313.4 & 0.701 & 0.7632\\
7 & 342 & -362789.9 & 726263.7 & 729035.9 & 727949.0 & 0.729 & 0.7702\\
8 & 391 & -362047.9 & 724877.9 & 728047.2 & 726804.6 & 0.737 & 0.8261\\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;}\\
\multicolumn{8}{l}{Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with}\\
\multicolumn{8}{l}{q-1 classes models.}\\
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-3}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccc}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Number of level 1 classes} \\
\cmidrule(l{2pt}r{2pt}){2-7}
Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Random effects model}}\\
\hspace{1em}2 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
\hspace{1em}3 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
\hspace{1em}4 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
\end{tabular}
\end{table}

### 2018-07-28 paper/main.tex
aims and objectives
strata weighting etc. added
tables 1 added
adding fig level 1 tables for model selection

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\addbibresource{summer.bib} % The filename of the bibliography
\DeclareRobustCommand{\firstsecond}[2]{#1}
\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\end{abbreviations}

>>>>

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
table]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\addbibresource{summer.bib} % The filename of the bibliography
\DeclareRobustCommand{\firstsecond}[2]{#1}
\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

%\usepackage[table]{xcolor}
\usepackage{colortbl} % to use colors for tables
\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
\usepackage{caption} % to change the font of the table titles

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------
\cleardoublepage\makeatletter\@openrightfalse\makeatother

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HbA1c} & \textbf{H}emoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}
